emmeans and varpred comparison

### 2021-10-07 compare_emmeans_varpred.rmd
Comparison plots

---
title: "Bias correction in GLMs"
author: Bicko, Jonathan & Ben
date: "2021 Oct 06 (Wed)"
compact-title: false
output:
  pdf_document:
    extra_dependencies: ["float"]
bibliography: bias_correction.bib
link-citations: yes
---

@@

```{r cont_no_interaction}
quants <- seq(0, 1, length.out=100)
focal_levels <- quantile(sim_df_cni$age, quants)
truth = c(truth=mean(sim_df_cni$hhsize))
print(truth)
compare_cni_plots <- (combinepreds(mod_cni, focal="age"
		, funs=c("emmeans", "varpred")
		, at=list(age=focal_levels)
		, x.var="age"
		, plotit=TRUE
	)
	+ geom_vline(aes(xintercept=mean(focal_levels)), lty=2, colour="grey")
)
print(compare_cni_plots)
```

@@

```{r cont_nwi_nf_interaction}
quants <- seq(0, 1, length.out=100)
focal_levels <- quantile(sim_df_wi_nf$age, quants)
truth = c(truth=mean(sim_df_wi_nf$hhsize))
print(truth)
compare_wi_nf_plots <- (combinepreds(mod_wi_nf, focal="age"
		, funs=c("emmeans", "varpred")
		, at=list(age=focal_levels)
		, x.var="age"
		, plotit=TRUE
	)
	+ geom_vline(aes(xintercept=mean(focal_levels)), lty=2, colour="grey")
)
print(compare_wi_nf_plots)
```

>>>>

---
title: "emmeans and varpred comparison"
author: Bicko, Jonathan & Ben
date: "2021 Oct 06 (Wed)"
compact-title: false
output:
  pdf_document:
    extra_dependencies: ["float"]
bibliography: bias_correction.bib
link-citations: yes
---

@@

```{r cont_no_interaction, fig.cap="Continuous: no interaction"}
quants <- seq(0, 1, length.out=100)
focal_levels <- quantile(sim_df_cni$age, quants)
print("Truth:")
print(true_prop_cni)
compare_cni_plots <- (combinepreds(mod_cni, focal="age"
		, funs=c("emmeans", "varpred")
		, at=list(age=focal_levels)
		, x.var="age"
		, plotit=TRUE
	)
	+ geom_vline(aes(xintercept=mean(focal_levels)), lty=2, colour="grey")
)
print(compare_cni_plots)
```

@@

```{r cont_wi_nf_interaction, fig.cap="Continuous: non-focal predictors interaction"}
focal_levels <- quantile(sim_df_wi_nf$age, quants)
print("Truth:")
print(true_prop_wi_nf)
compare_wi_nf_plots <- (combinepreds(mod_wi_nf, focal="age"
		, funs=c("emmeans", "varpred")
		, at=list(age=focal_levels)
		, x.var="age"
		, plotit=TRUE
	)
	+ geom_vline(aes(xintercept=mean(focal_levels)), lty=2, colour="grey")
)
print(compare_wi_nf_plots)
```

\subsection{Interaction between focal and non-focal predictors}

```{r cont_wi_f_interaction, fig.cap="Continuous: interaction betweem focal and non-focal predictors"}
focal_levels <- quantile(sim_df_wi_f$age, quants)
print("Truth:")
print(true_prop_wi_f)
compare_wi_f_plots <- (combinepreds(mod_wi_f, focal="age"
		, funs=c("emmeans", "varpred")
		, at=list(age=focal_levels)
		, x.var="age"
		, nesting="wealthindex %in% age"
		, plotit=TRUE
	)
	+ geom_vline(aes(xintercept=mean(focal_levels)), lty=2, colour="grey")
)
print(compare_wi_f_plots)
```

\section{Categorical predictors}

```{r catni, fig.cap="Categorical: no interaction"}
compare_catni_plots <- (combinepreds(mod_catni, focal="gender"
		, funs=c("emmeans", "varpred")
		, x.var="gender"
		, x.var.factor=TRUE
		, plotit=TRUE
	)
	+ geom_point(data=focal_prop_catni, aes(x=gender, y=hhsize), colour="black")
)
print(compare_catni_plots)
```
